The Strucplot Framework:\\ Visualizing Multi-way Contingency Tables with \pkg{vcd}

### 2005-11-02 trunk/vcd/paper/statreport22.Rnw
slight modifications in statreport
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@494 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\author{
  David Meyer \And Achim Zeileis \And Kurt Hornik
  \\
  Wirtschaftsuniversit\"at Wien
  }

@@

\fronttitle{The Strucplot Framework:\\ Visualizing Multi-way Contingency
  Tables with \pkg{vcd}}
\frontauthor{David Meyer, Achim Zeileis, Kurt Hornik}
\frontnumber{22}
\frontdate{November 2005}
\frontpage

@@

\begin{figure}[h]
\begin{center}
<<cellfig,fig=TRUE,echo=FALSE,width=7,height=7>>=
<<cell>>
@
\caption{Cell labeling for the \data{PreSex} data.}
\label{fig:cell}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
<<cell2fig,fig=TRUE,echo=FALSE>>=
<<cell2>>
@
\caption{Cell labeling for the \data{PreSex} data, labels abbreviated.}
\label{fig:cell2}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
<<conditionalfig,fig=TRUE,echo=FALSE>>=
<<conditional>>
@
\caption{Conditional labeling for the \data{PreSex}, labels abbreviated.}
\label{fig:conditional}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
<<textfig,fig=TRUE,echo=FALSE>>=
<<text>>
@
\caption{User-supplied Text added to a mosaic display of the \data{Titanic} data.}
\label{fig:text}
\end{center}
\end{figure}

@@

\setkeys{Gin}{width=0.8\textwidth}
\begin{figure}[h]
\begin{center}
<<listfig,fig=TRUE,echo=FALSE>>=
<<list>>
@
\caption{Labels indicated below the plot.}
\label{fig:list}
\end{center}
\end{figure}

@@

\begin{appendix}

>>>>

\author{
  \hfill David Meyer \hfill Achim Zeileis \hfill Kurt Hornik \hfill
  \\
  Wirtschaftsuniversit\"at Wien
  }

@@

\fronttitle{The Strucplot Framework: Visualizing Multi-way Contingency
  Tables with vcd}
\frontauthor{David Meyer, Achim Zeileis, Kurt Hornik}
\frontnumber{22}
\frontdate{November 2005}
\frontpage

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[p]
\begin{center}
<<cellfig,fig=TRUE,echo=FALSE>>=
<<cell>>
@
\caption{Cell labeling for the \data{PreSex} data.}
\label{fig:cell}
\end{center}
\end{figure}

@@

\begin{figure}[p]
\begin{center}
<<cell2fig,fig=TRUE,echo=FALSE>>=
<<cell2>>
@
\caption{Cell labeling for the \data{PreSex} data, labels abbreviated.}
\label{fig:cell2}
\end{center}
\end{figure}

@@

\begin{figure}[p]
\begin{center}
<<conditionalfig,fig=TRUE,echo=FALSE>>=
<<conditional>>
@
\caption{Conditional labeling for the \data{PreSex}, labels abbreviated.}
\label{fig:conditional}
\end{center}
\end{figure}

@@

\begin{figure}[p]
\begin{center}
<<textfig,fig=TRUE,echo=FALSE>>=
<<text>>
@
\caption{User-supplied Text added to a mosaic display of the \data{Titanic} data.}
\label{fig:text}
\end{center}
\end{figure}

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[p]
\begin{center}
<<listfig,fig=TRUE,echo=FALSE>>=
<<list>>
@
\caption{Labels indicated below the plot.}
\label{fig:list}
\end{center}
\end{figure}

@@

\clearpage
\begin{appendix}
